Validation failed EVT

### 2023-03-30 analysis/article-results.Rmd
Testing smaller and higher res figs

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = here::here())
knitr::opts_chunk$set(
  echo = FALSE, 
  out.width = "100%", 
  warning = FALSE, 
  message = FALSE
)

>>>>

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = here::here())

knitr::opts_chunk$set(
  echo = FALSE, 
  out.width = "70%", 
  warning = FALSE, 
  message = FALSE,
  fig.retina = 2L
)
